Home Nighttime Cough Monitoring

### 2024-10-09 Lilah Melzer/cough_monitor_analysis.qmd
Update cough_monitor_analysis.qmd

---
title: "Home Nighttime Cough Monitoring"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Documents/Miscellaneous/zotero.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup}
#| include: false
library(Hmisc)
library(tidyverse)
library(lubridate)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring",
  "Windows" = "C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/timvigers/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
#| message: false
# Import REDCap data
source(paste0(github_dir, "/CF/Lilah Melzer/cough_monitor_import.r"))
# Import counts
agg_counts <- read.csv(
  "./Data_Raw/Cough_w_TotalCounts_0824 - Cough_agg_w_count_0828.csv",
  na.strings = c("", "NMD"), header = F
)
# Format aggregated count data
agg_counts <- data.frame(t(agg_counts))
colnames(agg_counts) <- agg_counts[1, ]
agg_counts$`Date/Device` <- NULL
agg_counts <- agg_counts[-1, ]
colnames(agg_counts)[1] <- "sid"
agg_counts$sid <- sub("FN", "", agg_counts$sid)
# Wide to long, fix dates, count number of nights
agg_counts <- agg_counts %>%
  pivot_longer(cols = -one_of("sid"), names_to = "Date", values_to = "Coughs") %>%
  filter(!is.na(Coughs)) %>%
  mutate(Date = mdy(Date),
    Coughs = as.numeric(Coughs))%>%
  group_by(sid) %>%
  mutate(
    Night = row_number()
  ) %>%
  ungroup()
```

@@

```{r}
#| label: tbl-mean-demo
#| tbl-cap: Participant characteristics
```

@@

```{r}
#| label: tbl-mean-coughs
#| tbl-cap: Mean coughs per night
```

@@

```{r}
#| label: fig-coughs-by-night
#| fig-cap: Coughs by date
ggplot(agg_counts, aes(x = Date, y = Coughs, group = sid, color = sid)) +
  geom_point() +
  geom_line(alpha = 0.1) +
  theme(legend.position = "None")
```

@@

#

>>>>

---
title: "Home Nighttime Cough Monitoring"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Dropbox/Miscellaneous/zotero.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup}
#| include: false
library(Hmisc)
library(tidyverse)
library(lubridate)
library(arsenal)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring",
  "Windows" = "C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Home Nighttime Cough Monitoring"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/timvigers/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
#| message: false
# Import REDCap data
source(paste0(github_dir, "/CF/Lilah Melzer/cough_monitor_import.r"))
# Import counts
agg_counts <- read.csv(
  "./Data_Raw/Cough_w_TotalCounts_0824 - Cough_agg_w_count_0828.csv",
  na.strings = c("", "NMD"), header = F
)
# Format aggregated count data
agg_counts <- data.frame(t(agg_counts))
colnames(agg_counts) <- agg_counts[1, ]
agg_counts$`Date/Device` <- NULL
agg_counts <- agg_counts[-1, ]
colnames(agg_counts)[1] <- "sid"
agg_counts$sid <- sub("FN", "", agg_counts$sid)
# Wide to long, fix dates, count number of nights
agg_counts <- agg_counts %>%
  pivot_longer(cols = -one_of("sid"), names_to = "Date", values_to = "Coughs") %>%
  filter(!is.na(Coughs)) %>%
  mutate(
    Date = mdy(Date),
    Coughs = as.numeric(Coughs)
  ) %>%
  group_by(sid) %>%
  mutate(
    Night = row_number()
  ) %>%
  ungroup()
# Demographics data
data$Diagnosis <- factor(sub(".*arm_*", "", data$redcap_event_name),
  levels = 1:2,
  labels = c("CF", "Non-CF")
)
demo <- data %>%
  group_by(sid) %>%
  filter(row_number() == 1) %>%
  select(
    sid, Diagnosis, age_at_consent, height, weight,
    nih_sex.factor:nih_ethnicity.factor, mutation1.factor, mutation2.factor,
    cftr_mod.factor, cftr_mod_type.factor, mucolytic.factor:antih.factor
  )
# Set table options for the document
mycontrols <-
  tableby.control(numeric.stats = c("Nmiss2", "meansd", "medianq1q3", "range"))
```

@@

```{r results='asis'}
#| label: tbl-mean-demo
#| tbl-cap: Participant characteristics
f <- as.formula(paste0("Diagnosis ~", paste0(colnames(demo), collapse = "+")))
f <- update(f, . ~ . - Diagnosis - sid)
t1 <- tableby(f, data = demo, control = mycontrols)
summary(t1, pfootnote = T)
```

@@

```{r results='asis'}
#| label: tbl-mean-coughs
#| tbl-cap: Mean coughs per night
```

@@

```{r}
#| label: fig-coughs-by-date
#| fig-cap: Coughs by date
ggplot(agg_counts, aes(x = Date, y = Coughs, group = sid, color = sid)) +
  geom_point() +
  geom_line(alpha = 0.1) +
  theme(legend.position = "None")
```

@@
